---
title: "HPC Parallel Programming Workshop"
subtitle: "July 13-15, 2021"
author: "Yue Yu and Alex Pacheco"
institute: "Department of Mathematics and Library & Technology Services<br />Lehigh University"
date: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    chakra: libs/remark-latest.min.js
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:10"
      yolo: false
      beforeInit: "addons/imgscale.js"
    css: [addons/lehigh.css, addons/lehigh-fonts.css]
---
class: myback

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(tidyverse)
library(knitr)
knitr::opts_chunk$set(echo = TRUE, fig.width = 12, fig.height = 6)
```
```{r xaringan-webcam, include = FALSE}
#xaringanExtra::use_webcam()
xaringanExtra::use_xaringan_extra(c("tileview", "webcam"))
```

# Workshop Schedule

|   Day   |    Time    |     Session   |
|:-------:|:----------:|:-------------:|
| July 13 | 9AM - 12PM | Introduction to HPC & Linux |
|         | 1PM -  2PM | Research Talk: Xiu Yang, <br />Industrial & Systems Engineering, Lehigh University |
|         | 2PM -  5PM | Parallel Programming Concepts |
| July 14 | 9AM - 12PM | Introduction to OpenMP |
|         | 1PM -  2PM | Research Talk: Emily Johnson, <br />Aerospace & Mechanical Engineering, University of Notre Dame|
|         | 2PM -  5PM | Introduction to OpenACC |
| July 15 | 9AM - 12PM | Introduction to MPI |
|         | 1PM -  5PM | MPI (contd), Additional Exercise Time |

* 8:50AM - 9AM check in on all days with a break for lunch between Noon and 1PM.
* Computing time for Workshop provided by [NSF CC&#42; award 2019035](https://www.nsf.gov/awardsearch/showAward?AWD_ID=2019035&HistoricalAwards=false).
* Attendees will have access to HPC resources until August 31, 2021.


---

# Attendee Summary

```{r echo=FALSE, warning=F, message=F}
status <- tribble(
                   ~"Status",~"Count",~"Yes",~"No",
                   "Graduate",24,14,10,
                   "Undergraduate",5,1,4,
                   "Faculty",3,1,2,
                   "Postdoc/Staff",2,2,0
                  )
department <- tribble(
                     ~"Department", ~"Count",
                      "Mechanical Engineering",16,
                      "Computer Science",1,
                      "Mathematics",4,
                      "Electrical and Computer Engineering",1,
                      "Applied Mathematics",1,
                      "Industrial and Systems Engineering",5,
                      "Computer Science and Business ",1,
                      "Civil Enigneering",2,
                      "Computer Science and Engineering",1,
                      "ATLSS",1,
                      "LTS",1
                     )
language <- tribble(
                   ~"Language",~"Count",
                    "Fortran",6,
                    "C",19,
                    "C++",14,
                    "MATLAB",27,
                    "Python",25,
                    "R",9,
                    "Java",13,
                    "C#",1,
                    "Rust",1
                   )
lingo <- tribble(
                ~"Languages",~"Number",
                 "1",2,
                 "2",6,
                 "3",9,
                 "4",13,
                 "5",2,
                 "6",2
                )
```

```{r echo =F, warning=F}
suppressMessages(suppressWarnings(library(plotly)))
suppressMessages(suppressWarnings(
  plot_ly(status, labels=~Status, values=~Count, type = 'pie', textinfo = "values", text = status$Count) %>%
    layout(plot_bgcolor='#F1E7C8', paper_bgcolor='#F1E7C8')
))
```

---

# Attendee Summary

```{r echo =F, warning=F}
suppressMessages(suppressWarnings(library(plotly)))
suppressMessages(suppressWarnings(
  plot_ly(status, x=~Status, y=~Yes, type = 'bar', name="Yes") %>%
    add_trace(y=~No, name="No") %>%
    layout(plot_bgcolor='#F1E7C8', paper_bgcolor='#F1E7C8', xaxis = list(title=""), yaxis = list(title="HPC Experience"), barmode = 'group')
))
```

---

# Attendee Summary


```{r echo =F, warning=F}
suppressMessages(suppressWarnings(library(plotly)))
suppressMessages(suppressWarnings(
  plot_ly(department, x=~Department, y=~Count, type = 'bar') %>% 
    layout(legend = list(orientation = 'h')) %>%
    layout(plot_bgcolor='#F1E7C8', paper_bgcolor='#F1E7C8', xaxis = list(title=""), yaxis = list(title=""))
))
```


---

# Attendee Summary


```{r echo =F, warning=F}
suppressMessages(suppressWarnings(library(plotly)))
suppressMessages(suppressWarnings(
  plot_ly(language, x=~Language, y=~Count, type = 'bar') %>% 
    layout(legend = list(orientation = 'h')) %>%
    layout(plot_bgcolor='#F1E7C8', paper_bgcolor='#F1E7C8', xaxis = list(title=""), yaxis = list(title=""))
))
```


---

# Attendee Summary


```{r echo =F, warning=F}
suppressMessages(suppressWarnings(library(plotly)))
suppressMessages(suppressWarnings(
  plot_ly(lingo, x=~Languages, y=~Number, type = 'bar') %>% 
    layout(legend = list(orientation = 'h')) %>%
    layout(plot_bgcolor='#F1E7C8', paper_bgcolor='#F1E7C8', xaxis = list(title="Number of Languages"), yaxis = list(title=""))
))
```

---

# HPC Workshop 

* We have reserved the hawkgpu nodes for this workshop
* Only request as many resources as you need
      * Maximum of 6 cpus, 30 min walltime, and 1 gpu per job
* To run jobs interactively
```{bash eval=F}
srun -p hawkgpu -n 6 -N 1 --gres=gpu:1 -t 30 -A hpc2021_prog_083121 <program name>
```

* Example submit script
```{bash eval=F}
#!/bin/bash

#SBATCH -p hawkgpu
#SBATCH -n 6 -N 1
#SBATCH --gres=gpu:1
#SBATCH -t 30
#SBATCH -A hpc2021_prog_083121

<program name>
```

---

# Workshop Material

* Copy Workshop material to your current location
```{bash eval=F}
cp -r /home/alp514/Workshop/2021HPC/parprog .
```

* Directory Contents
   * `get_started`: for users who haven't used HPC or compiled code to get started with using Hawk 
   * `exercises`: sample serial codes to parallelize 
   * `solution`: directory containing solutions for exercises
* You have a choice of using GNU, Intel and NVIDIA HPC SDK compiler.
   * OpenACC: requires NVIDIA HPC SDK
* Exercise folder contains Makefiles that default to NVIDIA HPC SDK
* To use other compilers, specify the compiler as follows
```{bash eval=F}
make -f Makefile_c COMP=gnu
make -f Makefile_f90 COMP=intel
```
